Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-09 Cover_letter_JPM.tex
Updates from Overleaf

We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
= 詳細描述 univariable and multivariable tests work in the Cox proportional hazard regression model.
In a multivariable test, which variables were used? 
= 列出來，並且強調 surgical margin

% x
In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors. (please also see Figure \ref{fig:workflow}, different sources of databases)

The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]
%(the revised portions in the manuscript are indicated in \textcolor{red}{red} since page 2 at line 77-129)

%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga
% adopted from materials and methods

%The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
%\cite{SeanDavis;MartinMorgan2020}

@@

\begin{MyColorPar}{red}

"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."

\end{MyColorPar}   % marked in red above

@@

\subsection*{2-5}
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
=> = a gene signature with deep learning CNN
https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z

@@

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.

@@

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
[Minor comments]
The background should be revised extensively. 
x For example, the description of the linear model should be removed. X1...Xn should be removed. 
***More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be moved to Methods.

In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 
In Figure 1, the diagram should have direction. 
加上 direction of view

The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)???

In Figure 2, the ticks and labels on the x-axis were corrected.

\begin{MyColorPar}{red}

>>>>

We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]
%\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while

The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data. It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:

%Highlights
% https://quicklatex.com
\begin{flushleft}
% equation
%\begin{math}

$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
% natural exponential function => y=e^x
\end{flushleft}
where,\\
\begin{outline} % for highlight
\1 t represents the survival time
\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g. clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
\1 the term $h_0$ is called the baseline hazard. It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1). The ‘t’ in $h(t)$ indicates the hazard may vary over time
\end{outline}

Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]

Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).

In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
%\end{MyColorPar}

% x
%In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors. (please also see Figure \ref{fig:workflow}, different sources of databases)

%(the revised portions in the manuscript are indicated in \textcolor{red}{red} since page 2 at line 77-129)

@@

%"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."

%\end{MyColorPar}   % marked in red above

@@

\subsection*{2-5}
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.

We appreciate the reviewer for the critical comments.
*** => a gene signature with deep learning CNN
https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z

@@

@@

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
The description of the linear model has been removed. 
Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
We made a new Figure 1 with clear direction of the workflow.
A "gene expression values (20500 genes)", instead of "RNAseq", indicates the expression data obtained from the TCGA.
In Figure 2, the ticks and labels on the x-axis were corrected.

***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section. 
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
%\subsubsection{utility of TCGA}
%%%
Usually, researchers used TCGA to find expression biomarkers...
%%%%%%%%%

***[latex line 410]
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
=> First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned. 
After detailed 梳理, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500)
The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 謙虛道歉，修改說法

The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
%%%
=>  However, there are three steps of biomarker discovery from survival analysis.
***=> Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage. 這個 要改為 reviewer's comment (risk of maximizing P-value with cutoff scan)
...
